TCP Congestion Algorithms In Datacenters \\ {\large Large Systems $\cdot$ Project Report}

### 2017-12-24 paper/paper.tex
paper: consistent "vs." usage and fixing our names in the references

\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage[hyperref=true, natbib=true, style=numeric, backend=bibtex]{biblatex}
\usepackage{graphicx}
\bibliography{references.bib}
\usepackage[top=3.5cm, bottom=3.5cm, left=4.3cm, right=4.3cm]{geometry}

@@

\begin{figure}[H]
	\makebox[\textwidth]{
		\centering
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/cubic_vs_bic_8_0.png}
			\caption{CUBIC vs BIC with 8ms latency and 0\% loss}
			\label{fig:fair-1}
		\end{minipage}\hfill
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/dctcp-bic-8-0.png}
			\caption{DCTCP vs BIC with 8ms latency and 0\% loss}
			\label{fig:fair-2}
		\end{minipage}
	}
\end{figure}

@@

\begin{figure}[H]
	\makebox[\textwidth]{
		\centering
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/cubic_vs_bbr_8_12.png}
			\caption{CUBIC vs. BBR with 8ms latency and 1.2\% loss}
			\label{fig:bbr-cubic}
		\end{minipage}\hfill
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/cubic_vs_bic_8_12.png}
			\caption{CUBIC vs BIC with 8ms latency and 1.2\% loss}
			\label{fig:bic-cubic}
		\end{minipage}
	}
\end{figure}

>>>>

\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks, pdfauthor={Luc Gommans and Rick van Gorp}, pdftitle={TCP Congestion Algorithms in Datacenters}]{hyperref}
\usepackage[hyperref=true, natbib=true, style=numeric, backend=bibtex]{biblatex}
\usepackage{graphicx}
\bibliography{references.bib}
\usepackage[top=3.5cm, bottom=3.5cm, left=4.3cm, right=4.3cm]{geometry}

@@

\begin{figure}[H]
	\makebox[\textwidth]{
		\centering
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/cubic_vs_bic_8_0.png}
			\caption{CUBIC vs. BIC with 8ms latency and 0\% loss}
			\label{fig:fair-1}
		\end{minipage}\hfill
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/dctcp-bic-8-0.png}
			\caption{DCTCP vs. BIC with 8ms latency and 0\% loss}
			\label{fig:fair-2}
		\end{minipage}
	}
\end{figure}

@@

\begin{figure}[H]
	\makebox[\textwidth]{
		\centering
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/cubic_vs_bbr_8_12.png}
			\caption{CUBIC vs. BBR with 8ms latency and 1.2\% loss}
			\label{fig:bbr-cubic}
		\end{minipage}\hfill
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/cubic_vs_bic_8_12.png}
			\caption{CUBIC vs. BIC with 8ms latency and 1.2\% loss}
			\label{fig:bic-cubic}
		\end{minipage}
	}
\end{figure}
